\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2012-03-02 doc/USER_MANUAL/manual_SPECFEM3D.tex
removed "Cray"
added more details about "relocation truncated to fit"

\begin{description}
\item [{\texttt{Intel ifort compiler}}] See if you need to add \texttt{-assume byterecl} for your machine.
\item [{\texttt{IBM or Cray compilers}}] See if you need to add \texttt{-qsave} or \texttt{-qnosave} for your machine.
\item [{\texttt{Mac OS}}] You will probably need to install \texttt{XCODE}.
In addition, the \texttt{clock\_gettime} routine, which is used by the \texttt{SCOTCH} library that we use, does not exist in Mac OS.
You will need to replace it with \texttt{clock\_get\_time} if you want to use \texttt{SCOTCH}.
\end{description}

@@

If you run very large meshes on a relatively small number
of processors, the memory size needed on each processor might become
greater than 2 gigabytes, which is the upper limit for 32-bit addressing.
In this case, on some compilers you may need to add \texttt{``-mcmodel=medium}''
to the compiler options otherwise the compiler will display an error
message (for instance \texttt{``relocation truncated to fit: R\_X86\_64\_PC32 against .bss''} or something similar);
on an IBM machine with the \texttt{xlf} and \texttt{xlc} compilers, using \texttt{-q64} is usually sufficient.\\

>>>>

\begin{description}
\item [{\texttt{Intel ifort compiler}}] See if you need to add \texttt{-assume byterecl} for your machine.
\item [{\texttt{IBM compiler}}] See if you need to add \texttt{-qsave} or \texttt{-qnosave} for your machine.
\item [{\texttt{Mac OS}}] You will probably need to install \texttt{XCODE}.
In addition, the \texttt{clock\_gettime} routine, which is used by the \texttt{SCOTCH} library that we use, does not exist in Mac OS.
You will need to replace it with \texttt{clock\_get\_time} if you want to use \texttt{SCOTCH}.
\end{description}

@@

If you run very large meshes on a relatively small number
of processors, the memory size needed on each processor might become
greater than 2 gigabytes, which is the upper limit for 32-bit addressing.
In this case, on some compilers you may need to add \texttt{``-mcmodel=medium}''
to the compiler options of CFLAGS, FCFLAGS and LDFLAGS otherwise the compiler will display an error
message (for instance \texttt{``relocation truncated to fit: R\_X86\_64\_PC32 against .bss''} or something similar);
on an IBM machine with the \texttt{xlf} and \texttt{xlc} compilers, using \texttt{-q64} is usually sufficient.\\
